\textbf{Designing a Virtual Security Layer for Cloud Content}

### 2015-10-14 tex/paper.tex
Added JPF results

\subsubsection{REST}
Over http? WebSockets? 
\subsubsection{TODO: Insert persistent storage here}
    TODO: Write down related terminology, if any
\subsection{Abbreviations}

@@

\section{Related Work}
\subsection{Copy-on-Write}
This work relies heavily on the Copy-on-Write principle which was founded and used in the Mach kernel~\cite{COPYONWRITE}. 
Today Copy-on-Write is used in everything from file systems~\cite{BTRFS} to desktop compositors~\cite{COMPOSITOR}.

@@

What is needed
* Security layers
* Views
* Virtual file structure
* Versioning of content
* Multi project support
* Auth and audit logs
* Users
\newpage 
\section{Model}
\newpage 
\subsection{Entities}
%\subsubsection*{View} for not having section numbers
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.8]{relation.pdf}}
    \caption{Entity Relationships}
    \label{fig:relation}
\end{figure}

@@

\newpage 
\section{Copy-on-Write}

@@

\section{Resulting system}
\subsection{Persistent storage}
\subsubsection{MongoDB}

>>>>

\subsubsection{REST}
\subsubsection{MongoDB}
    TODO: Write down related terminology, if any
\subsection{Abbreviations}

\subsubsection{JPF}
Java Path Finder - It was developed by NASA and in 2005 they released it under an open source licence, which made more 
people contribute to the project. JPF is usually used for doing model checking of concurrent programs to easily find 
for example race conditions and dead locks.

@@

\section{Related Work}
\subsection{Copy-on-Write}
This work relies heavily on the Copy-on-Write principle which was founded and used in the Mach kernel~\cite{COPYONWRITE}.

Copy-on-Write is used in virtual memory management systems~\cite{VIRTCOW}, snapshot functionality in both file 
systems~\cite{FSCOW} and logical volume management systems~\cite{LVMCOW}, and as an optimisation technique for objects and 
types in programming languages\cite{LANGCOW}.

@@

What is needed
* Security layers
* Views
* Virtual file structure
* Versioning of content
* Multi project support
* Auth and audit logs
* Users
\newpage 
\section{Model}
\subsection{Entities}
%\subsubsection*{View} for not having section numbers
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.8]{relation.pdf}}
    \caption{Entity Relationships}
    \label{fig:relation}
\end{figure}

@@

\subsection{JPF}
Java path finder was used to show that the model and plan of how to build the system was sound. The model was built in Java 
with the objective of being as reduced and simple as possible, without loosing any of the cases that needs to be covered 
by the model checker.

Each collection in the persistent storage was emulated by using the built-in ConcurrentHashMap type. 
Each client was represented by a thread and each action taken by the client was randomised. The id hashes which MongoDB is 
using for each entity was imported from the mongo-java-driver-2.13.3 and each object had its own id, generated in the same 
fashion as the real implementation is using, randomly generated by the ObjectId class to minimise collisions that is. 
Further more no locking or transactions were used and the threads were running fully concurrently, without any sleep statements.

JPF checked each permutation of states that the threads can end up in, the result of the run can be seen in Listing~\ref{JPFRESULT}.

\begin{lstlisting}[label=JPFRESULT,caption=Results of JPF run]
elapsed time:       14:26:53
states:             new=160853259,
                    visited=451102505,
                    backtracked=611955764,
                    end=21640
search:             maxDepth=380,
                    constraints=0
choice generators:  thread=160853255 
                    (signal=0,
                    lock=3603938,
                    sharedRef=146989208,
                    threadApi=3,
                    reschedule=10260106), 
                    data=0

heap:               new=676056850,
                    released=435060996,
                    maxLive=655,
                    gcCycles=523950061

instructions:       11917045758
max memory:         6256MB
loaded code:        classes=111,
                    methods=2179
\end{lstlisting}

\newpage 
\section{Copy-on-Write}
As the persistent storage does not implement transactions or locks a lot of different problems can occur when several 
clients are working on the same data set at the same time. Such problems could be race conditions,

@@

\section{Resulting system}
\subsection{Persistent storage}
\subsubsection{MongoDB}
MongoDB was chosen as the persistent storage because of its internal storage format called BSON, which is very similar to JSON 
which the API is using. As the formats are similar, the process of marshalling and unmarshalling becomes quite easy between 
the core code, MongoDB instance and REST interface. The second reason was that if the system needs to scale in the future it 
is very easy to distribute MongoDB and if needed the system can easily be migrated to Reactive Mongo, which is asynchronous and 
non-blocking and can therefore scale even further~\cite{REACTIVEMONGO}.
